---
title: "task4"
author: "Mattia Storero"
date: "17/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(kableExtra)
library(ggplot2)
library(knitr)
library(scales)
library(dplyr)
library(forecast)
library(readxl)
library(ggpubr)
```




## BACKGROUND

Firstly, the data was downloaded from "http://ansatte.uit.no/oystein.myrland/data/storedata.csv" and then analysed.
```{r, include=FALSE}
rm(list = ls())
data = read.csv("http://ansatte.uit.no/oystein.myrland/data/storedata.csv", header = TRUE)

data <- data %>% mutate(Order_Date = as.Date(Order_Date),
         year = lubridate::year(Order_Date),
         month = lubridate::month(Order_Date))

```

## FIRST TASK

For the last 3 months of 2017 were calculated the total sales by month, for region 1 and 9 and for some parts of the Customer_segment ("corporate" and "Consumer"). The final output will be called Table1.

```{r echo=FALSE, message=FALSE, warning=FALSE}
data1 <- data[which(data$year=="2017"), ]


data1 <- data1[data1$Region=="Region 1" | data1$Region=="Region 9", ]
data1 <- data1[data1$month=="10"|data1$month=="11"|data1$month=="12", ]
data1 <- data1[data1$Customer_Segment=="Corporate"|data1$Customer_Segment=="Consumer", ]

data1 <- data1 %>% group_by(month, Region, Customer_Segment) %>%
  summarise(TOTSales = sum(Sales))

Table1 <- kable(data1) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

Table1
```

## SECOND TASK

After that, a plot of the monthly total sales was made for Region 1 and 13 in 2015, 2016 and 2017. The final output will be called Figure1.
```{r echo=FALSE, message=FALSE, warning=FALSE}
data2 <- data[which(data$year=="2015"|data$year=="2016"|data$year=="2017"), ]


data2 <- data2[data2$Region=="Region 1" | data2$Region=="Region 13", ]

data2 <- data2 %>% group_by(year, month, Region) %>%
  summarise(TOTSales = sum(Sales))
data2 <- data2 %>% mutate(date = as.Date(lubridate::ymd(paste(year,month,01)))) 

Figure1 <- ggplot(aes(y = TOTSales, x = date, color = Region),
      data = data2) +
  labs(x="year", y="TOTSales") + geom_line() +
  ggtitle("Monthly sales from 2015 to 2017") + scale_y_continuous(limits = c(0, 60000)) +  scale_x_date(breaks = date_breaks("months"), labels = date_format("%b-%y")) 


Figure1


```

## THIRD TASK

Then, the months in which the number of total Sales in Region 13 is greater than the total Sales in Region 1 were identified (in figure1). This output will be put in a table (Table2).

```{r echo=FALSE, message=FALSE, warning=FALSE}

data3 <- data2 
data3.1 <- data3 %>% filter(Region == "Region 1")
data3.13 <- data3 %>% filter(Region == "Region 13")
Table2 <- full_join(data3.1, data3.13, by="date") %>%
  mutate(diff = (TOTSales.y - TOTSales.x) > 0)
Table2 <- Table2 %>% filter(diff > 0)

kable(Table2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))


```

## FOURTH TASK

The average Profit per Customer_Segment and Product_Category was found for all regions(excepted 3, 5 and 8) in 2017.
To make it clearer, the Table3 was created. This last one represents the segment that produced the highest average profit.


```{r echo=FALSE, warning=FALSE}

data4 <- data[which(data$year=="2017"),]
data4 <-data4[!(data4$Region=="Region 3" | data4$Region=="Region 5") | data4$Region=="Region 8",]

data4 <- data4 %>% group_by(Product_Category, Customer_Segment) %>%
  summarise(Meanprofit = mean(Profit))                    

data4 <- data4 %>% 
    group_by(Customer_Segment) %>% 
    slice(which.max(Meanprofit))                    

Table3 <-  max(data4$Meanprofit, na.rm = TRUE)
Table3
                    
```
It's easy to see that the consumer segment with the highest profit is the Small Business one with a mean number of 544.4429.



## FIFTH TASK 

The last point was to estimate a SARIMA model on the aggregated monthly Order_Quantity in the Customer_Segment; Small Business and Product_Category; Office Supplies. The SARIMA model contains the following parameters:
p - AR order
d - difference order
q - MA order
P - SAR order
D - seasonal difference
Q - SMA order
S - seasonal period (12 months in these data)


The procedures were described in this way:
"Iterate p and q over 0,1,2,3,4, d over 0,1, P and Q over 0,1,2,3,4, D over 0,1, and keep S fixed at 12. This gives a total of 2500 models. Estimate these models on the monthly data from 2014 through 2016, and identify the best SARIMA model on a holdout sample from 2017, based on the smallest RMSE (Root Mean Square Error). Produce a plot of the whole time series, and add onto it the 2017 forecast from the best SARIMA model, together with the actual aggregated monthly Order_Quantity. This output is Figure 2. Specify what was the best SARIMA model on the plot."

```{r, include=FALSE}
#background of SARIMA MODEL
data5 <- data[data$Customer_Segment=="Small Business"& data$Product_Category=="Office Supplies", ]

data5 <- data5 %>% group_by(year, month) %>%
  summarise(sum.order.quantity = sum(Order_Quantity))    

data5.1 <- data5[data5$year=="2014"| data5$year=="2015"|data5$year=="2016", ]
data5.2 <- data5[data5$year=="2017", ]


```


```{r, include=FALSE}
tsdata5.1 <- ts(data5.1$sum.order.quantity, frequency = 12, start =c(2014,1), end = c(2016,12))

tsdata5.2 <- ts(data5.2$sum.order.quantity, frequency = 12, start =c(2017,1), end = c(2017,12))

plot(tsdata5.1)
plot(tsdata5.2)
#trying with normal parameters
#get the optimal one
autoarima1 <- auto.arima(tsdata5.1)
autoarima2 <- auto.arima(tsdata5.2)

forecast1 <- forecast(autoarima1, h=12)
forecast1
plot(forecast1)

ARIMAfit = auto.arima(diff(tsdata5.1), approximation=FALSE,trace=FALSE)
summary(ARIMAfit)


```


```{r echo=FALSE, warning=FALSE}
test1 <- arima(tsdata5.1, order = c(1,0,1), seasonal = c(1,1,0))
test.forecast1 <- forecast(test1, h=12)
Figure2.1 <- test.forecast1 %>% autoplot(xlab="Year", ylab="Quantity of Order",
    main="Quantity of orders from 2014 to 2016 with prevision")
Figure2.1

Figure2.2 <- ggplot(aes(y = sum.order.quantity, x = month),
      data = data5.2) +
  labs(x="month", y="quantity") + geom_line() +
  ggtitle("Quantity of orders in 2017")
Figure2.2


```

```{r, include=FALSE}

Figure2 <- ggarrange(Figure2.1, Figure2.2,
                    ncol = 1, nrow = 2)
Figure2

```



Figure2 consists in a comparison between the prevision and the efective data. It's possible to see that the the model didn't predict the results in a accurate way.



```{r, include=FALSE}
#iterating#notuseful
test <- Arima(tsdata5.1)
forecasttest <- forecast(test, h=12)
plot(forecasttest)
```

```{r eval=FALSE, include=FALSE}

#attempt to use the parametres assigned but error
p <- 0:4
q <- 0:4
P <- 0:4
Q <- 0:4
d <- 0:1
D <- 0:1

modellist <- list()
for (i in p){
  for (i in q){
    for (i in d){
      for (i in P){
        for (i in Q){
          for (i in D){
      modellist <- Arima(tsdata5.1, order=c(p,q,d), seasonal=c(P,D,Q), method="ML")  }}}}}}
```




